\section{Discussion}
\label{sec:discussion}

Our work combines ideas from deep convolutional neural networks and
fully-connected conditional random fields, yielding a novel method able to
produce semantically accurate predictions and detailed segmentation maps,
while being computationally efficient. Our experimental results show that the
proposed method significantly advances the state-of-art in the challenging
PASCAL VOC semantic image labeling task.

There are multiple aspects in our model that we intend to refine, with the most important being the 
full integration of its two main components (CNN and CRF) and training the whole
system in an end-to-end fashion.  In particular, we currently use a very naive form of piecewise training, which consists in first training the DCNN classifier, and then training the CRF while keeping the DCNN classifier fixed. But in principle the gradient of the CRF loss function can be back-propagated to the DCNN, while in recent work \citet{chen2014learning} we have exploired ways of efficiently blending inference and learning to jointly train DCNNs and CRFs. We intend to further pursue this direction in our future work. 
We also plan to experiment with more datasets
and apply our method to other sources of data such as depth maps or videos.

At a higher level, our work lies in the intersection of convolutional neural
networks and probabilistic graphical models. We plan to further investigate
the interplay of these two powerful classes of methods and explore their
synergistic potential for solving challenging computer vision tasks.
